---
title: "Evaluating Item Importance"
author: "Zehang Richard Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vaItemResponse Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 7, fig.align = "center")
library(vaItemResponse)
## library(ggplot)?
```

This vignette provides a minimal example of using simulated data to calculate item importance in VA questionnaires.

We first load a simulated dataset from the InterVA5 package

```{r}
library(vaItemResponse)
library(InterVA5)
data(RandomVA5)
```

When reference deaths are available in real data analysis, we can use the function `mapICD` in the package to map ICD-10 codes into WHO cause list. For example, 
```{r}
mapICD("A90")
```

For illustration purposes, we generate random causes-of-death for these deaths.

```{r, warning=FALSE}
random_COD <- data.frame(ID = RandomVA5$ID)
set.seed(1)
random_COD$cause = sample(c("Cause 1", "Cause 2", "Cause 3"), 
							dim(random_COD)[1], replace=TRUE)
```


Now we are ready to calculate the symptom importance metric. The first step is to reorganize the data and account for fixed dependence relationship between symptoms due to the skip patterns of the questionnaire, using the `organize_dependence` function. We then use the output and the `evaluate_symptom` to calculate the importance metric for a particular symptom.


```{r, warning=FALSE}
data <- organize_dependence(RandomVA5, COD = random_COD)
metric <- evaluate_symptom(data = data, symptom = "i147o")
metric
```

Notice this call of `evaluate_symptom` can take a long time to compute when the number of deaths and the number of causes are large. We can perform the calculation on a selected subset of causes as well. For example, 

```{r, warning=FALSE}
metric.sub <- evaluate_symptom(data = data, symptom = "i147o", 
							   causes.compute = c("Cause 1", "Cause 3"))
metric
```
